---
title: "Practicum"
output: html_notebook
author: "Raquel Buezo"
---
## Install packages
```{r}
install.packages('data.table')
install.packages('lubridate')
install.packages('corrplot')
```

## Load libraries
```{r}
library(data.table)
library(lubridate)
library(ggplot2)
library(corrplot)
library(anytime)
```

## Load historic logs and make first predictions
```{r}
setwd('~/Documents/Practicum/')

logs <- fread(file = './dataframes/historicLogData.csv', sep = ',', stringsAsFactors = TRUE, header = TRUE)

head(logs)
```

## Initial statistics
```{r}
summary(logs)
```

```{r}
str(logs)
```

## I see there are NAs so I clean the data
```{r}
# NAs in my data?
print("Data before cleaning:")
apply(logs, 2, function (x) sum(is.na(x)))

# Clean it
print("Data after cleaning:")
logs_cln <- na.omit(logs)
apply(logs_cln, 2, function (x) sum(is.na(x)))
```
## I see there are many values equal to -1 so I am going to look at them and remove them
```{r}
sum(logs_cln$usage_cpu==-1)
sum(logs_cln$usage_nwin==-1)
sum(logs_cln$usage_nwout==-1)

badData <- logs_cln[logs_cln$usage_cpu==-1,]
summary(badData)
```

```{r}
t1 <- anytime(range(badData$timestamp)[1])
t2 <- anytime(range(badData$timestamp)[2])
paste("Bad data from " , t1 , " to ", t2)
```

## See the distribution of the bad data
```{r}
ggplot(data = badData, aes(badData$timestamp))+
  geom_histogram(aes(fill=..count..)) +
  scale_fill_gradient("Count", low="blue", high="red")+ 
  labs(title="", x="date", y="Count of -1s")+
  facet_wrap(~badData$instance, strip.position = 'bottom', dir = 'v')
```


```{r}
logs_cln[logs_cln$usage_cpu==-1,] <- NA
apply(logs_cln, 2, function (x) sum(is.na(x)))
logs_cln <- na.omit(logs_cln)
apply(logs_cln, 2, function (x) sum(is.na(x)))
```
## Look at correlations 
```{r}
X3 <- logs_cln[,c('timestamp','usage_cpu','usage_nwin', 'usage_nwout')]
corr <- round(cor(X3),2)
corrplot(corr, type = "lower", method = "color", addCoef.col = "black")
```


## Simple regression model only with time & usage_cpu
```{r}
X <- logs_cln[, c('instance', 'timestamp','usage_cpu')]
test <- lm(usage_cpu~., X)
summary(test)
```

## Simple regression model adding usage_nwin, usage_nwout
```{r}
X2 <- logs_cln[, c('instance', 'timestamp','usage_cpu','usage_nwin', 'usage_nwout')]
test2 <- lm(usage_cpu~., X2)
summary(test2)
```
